A first look at the GD-1 stellar stream with Gaia DR2

### 2018-04-27 paper/gd1.tex
Stuff
Title

\title{Gaia DR2 view of the GD-1 stellar stream}

@@

Most of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 35^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd} shows the $V$-band extinction in the region around the
GD-1 stream, computed from the Schlegel-Finkbeiner-Davis extinction map
(\cite{Schlegel:1998}; hereafter SFD).
Vertical lines indicate the two regions clearly identifiable as under-densities
from the proper-motion-selected stream members.
The maximum $A_V$ is $\approx$0.07 mag in both the under-density and gap
regions.
The dispersion in $A_V$ in the region $-60^\circ < \phi_1 < 0^\circ$ and
$-1^\circ < \phi_1 < 1^\circ$ is $\std_{A_V} \approx 0.03~\textrm{mag}$.

>>>>

\title{A first look at the GD-1 stellar stream with Gaia DR2}

@@

Most of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 35^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd} shows the $V$-band extinction in the region around the
GD-1 stream, computed from the Schlegel-Finkbeiner-Davis extinction map
(\cite{Schlegel:1998}; hereafter SFD).
Vertical lines indicate the two regions clearly identifiable as under-densities
from the proper-motion-selected stream members.
The maximum $A_V$ is $\approx$0.07 mag in both the under-density and gap
regions.
The dispersion in $A_V$ in the region $-60^\circ < \phi_1 < 0^\circ$ and
$-1^\circ < \phi_1 < 1^\circ$ is $\sigma_{A_V} \approx 0.03~\textrm{mag}$.
